{{ cookiecutter.paper_title}}

### 2018-08-26 {{ cookiecutter.repo_name }}/Paper/paper.tex
Fixed error with underscore symbold. Reference: https://tex.stackexchange.com/questions/53399/is-it-necessary-to-escape-underscores-in-href-with-dollar-signs-or

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \mailto{{{ cookiecutter.author_email }}}}\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}

>>>>

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \href{mailto:{{ cookiecutter.author_email }}}{ {{ cookiecutter.author_email.replace('_', '\_' ) }} } }\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}
